Our peculiar motion across the Universe

### 2019-06-11 paper/main.tex
caption

\begin{figure*}
\begin{center}
  \includegraphics[width=0.9\textwidth]{cumulative_probability_18.pdf}
\end{center}
\caption{A}
\label{fig:proba}
\end{figure*}

>>>>

\begin{figure*}
\begin{center}
  \includegraphics[width=0.9\textwidth]{cumulative_probability_18.pdf}
\end{center}
\caption{Distributions of peculiar velocities for MW type halos
  (individual, paired and observed). 
  Left panel shows the estimated probability density.
  The right panel shows the cumulative probability density.
  Paired halos have a slightly lower peculiar velocity than isolated
  halos.
  The observed peculiar velocity ($v_p=627\pm22$ km s$^{-1}$) shown as
  the vertical shaded stripe, is always located on the high velocity
  tail of simulations.}
\label{fig:proba}
\end{figure*}
